\begin{abstract}
  
In this paper we apply neural networks and Artificial Intelligence
(AI) to historical records of high-risk cryptocurrency coins to train
a prediction model that guesses their price. This paper's code
contains Jupyter notebooks, one of which outputs a timeseries graph of
any cryptocurrency price once a CSV file of the historical data is
inputted into the program. Another Jupyter notebook trains an LSTM, or
a long short-term memory model, to predict a cryptocurrency's closing
price. The LSTM is fed the close price, which is the price that the
currency has at the end of the day, so it can learn from those
values. The notebook creates two sets: a training set and a test set
to assess the accuracy of the results.

The data is then normalized using manual min-max scaling so that the
model does not experience any bias; this also enhances the performance
of the model. Then, the model is trained using three layers- an LSTM,
dropout, and dense layer-minimizing the loss through 50 epochs of
training; from this training, a recurrent neural network (RNN) is
produced and fitted to the training set. Additionally, a graph of the
loss over each epoch is produced, with the loss minimizing over
time. Finally, the notebook plots a line graph of the actual currency
price in red and the predicted price in blue. The process is then
repeated for several more cryptocurrencies to compare prediction
models. The parameters for the LSTM, such as number of epochs and
batch size, are tweaked to try and minimize the root mean square
error.

\end{abstract}
